01_limma_voom

### 2019-03-19 scripts/01_limma_all.Rmd
add colored mds and tables for contrasts

@@

cont <- "FG_HL"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
#kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
c <- plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='Female gonad lay to hatch', frame.plot=F)

cont <- "FH_HL"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
#kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
a <- plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='Female hypothalamus lay to hatch', frame.plot=F)

cont <- "FP_HL"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
#kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
b <- plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='Female pituitary lay to hatch', frame.plot=F)

cont <- "MG_HL"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
#kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
f <- plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='Male gonad lay to hatch', frame.plot=F)

cont <- "MH_HL"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
#kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
d <- plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='Male hypothalamus lay to hatch', frame.plot=F)

cont <- "MP_HL"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
#kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
e <- plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='Male pituitary lay to hatch', frame.plot=F)

plot_grid(a,b,c,d,e,f, nrow = 2)

>>>>

```{r plotMDS-colored}
levels(colData$tissue)
col.tissue <- c("#7570b3","#d95f02", "#1b9e77")[colData$tissue]
plotMDS(parentalobject,col=col.tissue)
legend("bottomright",fill=c("#7570b3","#d95f02", "#1b9e77"),legend=levels(colData$tissue))
title("Colored by Tissue")

levels(colData$treatment)
col.treatment <- c("#a6cee3", "#1f78b4", "#b2df8a", "#33a02c", "#fb9a99", "#e31a1c", "#fdbf6f", "#ff7f00", "#cab2d6")[colData$treatment]
plotMDS(parentalobject,col=col.treatment)
legend("bottomright",fill=c("#a6cee3", "#1f78b4", "#b2df8a", "#33a02c", "#fb9a99", "#e31a1c", "#fdbf6f", "#ff7f00", "#cab2d6"),legend=levels(colData$treatment))
title("Colored by Treatment")

levels(colData$sex)
col.sex <- c("#5ab4ac","#d8b365")[colData$sex]
plotMDS(parentalobject,col=col.sex)
legend("bottomright",fill=c("#5ab4ac","#d8b365"),legend=levels(colData$sex))
title("Colored by Sex")
```

@@

cont <- "FG_HL"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='Female gonad lay to hatch', frame.plot=F)

cont <- "FH_HL"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='Female hypothalamus lay to hatch', frame.plot=F)

cont <- "FP_HL"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='Female pituitary lay to hatch', frame.plot=F)

cont <- "MG_HL"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
#kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='Male gonad lay to hatch', frame.plot=F)

cont <- "MH_HL"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='Male hypothalamus lay to hatch', frame.plot=F)

cont <- "MP_HL"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='Male pituitary lay to hatch', frame.plot=F)
```
